Quanta concentration and Transmission risk

### 2024-11-25 analysis/simulation-results.Rmd
updated simulation results

```{r}
# main quanta simulation files
main_qc <- data.frame(
  files = list.files("simulations/main",
    full.names = TRUE, pattern = "quanta_conc-.*.txt$",
    recursive = TRUE
  )
) %>%
  mutate(
    room = ifelse(grepl("Waiting", files), "Waiting room",
      ifelse(grepl("Corridor", files), "Corridor", "TB room")
    ),
    daytime = ifelse(grepl("morning", files), "morning", "afternoon")
  )

@@

# corresponding transmission risk
ir_sit <- (.5 * IR("sitting", "male") + .5 * IR("sitting", "female")) / 3600
wr_vol <- (cellSize / 1e3)^2 * dimWR[3]
wr_morn <- main_mean_qc %>%
  filter(room == "Waiting room", daytime == "morning") %>%
  pull(value) %>%
  max()
wr_noon <- main_mean_qc %>%
  filter(room == "Waiting room", daytime == "afternoon") %>%
  pull(value) %>%
  max()
round((1 - exp(-wr_morn * 3600 * ir_sit / wr_vol)) * 100, 3)
round((1 - exp(-wr_noon * 3600 * ir_sit / wr_vol)) * 100, 3)

@@

```{r}
# main simulation files
main_tr <- data.frame(
  files = list.files("simulations/main",
    full.names = TRUE, pattern = "trans-risk.txt$",
    recursive = TRUE
  )
)

@@

```{r}
# process tracking data
track_daytime <- track %>%
  mutate(h = lubridate::hour(time)) %>%
  group_by(date, patient_id) %>%
  summarize(
    dur_morning = sum(h < 12),
    dur_afternoon = sum(h >= 12),
    tracking_end = tracking_end[1]
  ) %>%
  ungroup() %>%
  mutate(daytime = ifelse(dur_morning > dur_afternoon, "Morning", "Afternoon"))

@@

```{r additional-analyses}
# IPC scenario files
files_nm <- list.files("simulations/nomasks",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_vent <- list.files("simulations/vent",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_nmvent <- list.files("simulations/nomasksvent",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)

@@

```{r} 
# prevalence scenario files
files_prev <- list.files("simulations/prevalence",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_susp <- list.files("simulations/suspected",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)

>>>>

```{r quanta-concentration}
# main quanta simulation files
main_qc <- data.frame(
  files = list.files("simulations/main",
    full.names = TRUE, pattern = "quanta_conc-.*.txt$",
    recursive = TRUE
  )
) %>%
  mutate(
    room = ifelse(grepl("Waiting", files), "Waiting room",
      ifelse(grepl("Corridor", files), "Corridor", "TB room")
    ),
    daytime = ifelse(grepl("morning", files), "morning", "afternoon")
  )

@@

# corresponding transmission risk
ir_sit <- (.5 * IR("sitting", "male") + .5 * IR("sitting", "female")) / 3600
wr_vol <- (cellSize / 1e3)^2 * dimWR[3]
wr_morn <- main_mean_qc %>%
  filter(room == "Waiting room", daytime == "morning") %>%
  pull(value) %>%
  max()
wr_noon <- main_mean_qc %>%
  filter(room == "Waiting room", daytime == "afternoon") %>%
  pull(value) %>%
  max()
round((1 - exp(-wr_morn * 3600 * ir_sit / wr_vol)) * 100, 2)
round((1 - exp(-wr_noon * 3600 * ir_sit / wr_vol)) * 100, 2)

@@

```{r main-transmission-risk}
# main simulation files
main_tr <- data.frame(
  files = list.files("simulations/main",
    full.names = TRUE, pattern = "trans-risk.txt$",
    recursive = TRUE
  )
)

@@

```{r association-risk-factors}
# process tracking data
track_daytime <- track %>%
  mutate(h = lubridate::hour(time)) %>%
  group_by(date, patient_id) %>%
  summarize(
    dur_morning = sum(h < 12),
    dur_afternoon = sum(h >= 12),
    tracking_end = tracking_end[1]
  ) %>%
  ungroup() %>%
  mutate(daytime = ifelse(dur_morning > dur_afternoon, "Morning", "Afternoon"))

@@

```{r ipc-comparison}
# IPC scenario files
files_nm <- list.files("simulations/nomasks",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_vent <- list.files("simulations/vent",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_nmvent <- list.files("simulations/nomasksvent",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)

@@

```{r sensitivity-prevalence} 
# prevalence scenario files
files_prev <- list.files("simulations/prevalence",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_susp <- list.files("simulations/suspected",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
